---
title: "Connor Rice"
author: "Fall 2023"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb = 2
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg


p <- ggplot(my1000, aes(x=k2),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 2") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```
## We expect the sample mean to be close to population and the standev to get smaller by the ratio of one to the sample size. In this case 1/sqrt(2)

### There are 3 peaks in the density plot. You pick two people you can get MM,MF.FM,or FF. these are all equally likey so the little peak on left is all the FF's while the little peak on the right is all the MM's so the big one in the middle is both the MF and FM in the same bag so-to-speak.  

`r mean(my1000$k2)`
`r sd(my1000$k2)`


```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```

### In this case the stdev was cut in half because the sample size was four. This is what the central limit theorem says. There are also 5 peaks. They go from FFFF,to FFFM, to FFMM to FMMM and finally MMMM.


```{r}
numb = 9
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k9 = x.avg


p <- ggplot(my1000, aes(x=k9),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k9)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k9),' sd = ',sd(my1000$k9)))

```

At a sample size of 9 the peaks have multiplied to the extent that they now appear as one singular peak. The standard deviation is now also about 1/3rd of the base sample, which is in track with the 1/sqrt(n) trend of the central limit theorem.

```{r}
numb = 16
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg


p <- ggplot(my1000, aes(x=k16),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k16)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 16") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```

At a sample size of 16 the peaks have multiplied to the extent that they now appear as one singular peak. The standard deviation is now also about 1/4th of the base sample, which is in track with the 1/sqrt(n) trend of the central limit theorem.

```{r}
numb = 25
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k25 = x.avg


p <- ggplot(my1000, aes(x=k25),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k25)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 25") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k25),' sd = ',sd(my1000$k25)))

```

At a sample size of 25 the peaks have multiplied to the extent that they now appear as one singular peak, the peak has also become more centralized around the mean-line. The standard deviation is now also about 1/5th of the base sample, which is in track with the 1/sqrt(n) trend of the central limit theorem.

```{r}
numb = 36
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg


p <- ggplot(my1000, aes(x=k36),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k36)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 36") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

At a sample size of 36 the peaks have multiplied to the extent that they now appear as one singular peak, the peak has also become more centralized around the mean-line. The standard deviation is now also about 1/6th of the base sample, which is in track with the 1/sqrt(n) trend of the central limit theorem.
